Increasing prevalence of plant-fungal symbiosis across two centuries of environmental change

### 2024-09-18 Manuscript/endo_herbarium.tex
adding caterpillar type plot for collector and scorer.

\begin{figure}[H]
	\centering
	\includegraphics[width = .8\linewidth]{../Plots/collector_posterior_plot.pdf}
	\caption{\textbf{Posterior estimates of collector random effects.} Density curves show the posterior estimate along lines indicating the 95\% CI for 12 randomly selected collectors.}
		\label{fig:collector_fx}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width = .8\linewidth]{../Plots/scorer_posterior_plot.pdf}
	\caption{\textbf{Posterior estimates of scorer random effects.} Density curves show the posterior estimate along lines indicating the 95\% CI for 25 scorers.}
	\label{fig:scorer_fx}
\end{figure}

>>>>

\begin{figure}[H]
	\centering
	\includegraphics[width = .6\linewidth]{../Plots/collector_posterior.png}
	\caption{\textbf{Posterior estimates of collector random effects.} Points show posterior median along with 95\% CI for each of $924$ individual collectors.}
		\label{fig:collector_fx}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width = .6\linewidth]{../Plots/scorer_posterior.png}
	\caption{\textbf{Posterior estimates of scorer random effects.} Points show posterior median along with 95\% CI for each of $25$ individual collectors.}
	\label{fig:scorer_fx}
\end{figure}
